---
title: "StationSim Results."
date: '`r format(Sys.time(), "%d %B, %Y (%H:%M)")`'
output:
  html_document: 
    toc: yes
    pandoc_args: [
      "+RTS", "-K64m", 
      "-RTS"
    ]
fontsize: 10pt
---

# Initialise 

```{r initialise, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(gtools)
library(ggplot2)
library(hexbin) # (this is called automatically if required, but putting it here ensures it has been installed)
library(gridExtra) # For arranging two grids side by side
#library(reshape2) # for melting (taking wide format and making it narrow)


homedir<-"/Users/nick/research_not_syncd/git_projects/keanu-post-hackathon/results/"
setwd(homedir)

dataDir = "./plot"

```

# Load Data

```{r laodData}
# Find files
samples_files <- grep("Samples_obInterval", list.files(path = dataDir), value=TRUE)
truth_file <-  grep("Truth", list.files(path = dataDir), value=TRUE)

#Ensure files are in correct order (mixed sort includes numerical sorting of embeded numbers)
samples_files <- mixedsort(unlist(samples_files))

# Read all the files in
samples <- map(samples_files, function(x) read_csv(paste("plot/", x, sep=""), col_names = FALSE))
truth <- read_csv(paste("plot/", truth_file[1], sep=""), col_names = FALSE)

# This should be greped instead
#obIntervals <- c(0,1,5,10)
#obIntervals <- c(0,1)
obIntervals <- c(0,1,3,5,10,15,20,25,30,40,50,60,70,80,90,100)
```

# Plot results

## Spaghetti plot

```{r spag.plot, fig.width=11, fig.height=9}
# Define a fucntion to plot the samples
spag_plot <- function(samples, truth, obs) {

  x_axis <- 1:ncol(samples)
  sample_col <- alpha("#ADD8E6", 0.9)
  truth_col <- "red"

  #create plot
  plot(1, xlim=c(0, max(x_axis)), ylim=c(0, max(samples)), type='l',
       xlab="Number of iterations", ylab = "Number of agents",
       main = paste("Observation Interval =", obs, sep =' '))
  map(1:nrow(samples), function(x) lines(x_axis, samples[x,], type='l', col=sample_col))
  lines(x_axis, truth, type='l', lwd=2.5, col = truth_col)

  legend("bottomright", c("Samples", "Truth"), lty=c(1,1), lwd=c(2.5,2.5),col=c(sample_col, truth_col))
}


par(mfrow=c(3,3))
map2(samples, obIntervals, function(x, obInterval) spag_plot(x, truth, obInterval))

```

## Density plot

Create the plots

```{r density.plot-create, cache=TRUE}

# Returns a single ggplot2 density plot
density_plot <- function(s, truth, obs) {
  
  # Y values for this sample (num people per iteration)
  y <- t(s[1,])[,1]
  # X values
  x <- 1:length(y)
  # A long two-column matrix will have number of people at every iteration across all samples
  scatter <- cbind(x, y)
  # Now add the rest of the samples
  for (i in 2:nrow(s)) {
    scatter <- rbind(scatter, cbind(1:length(y), t(s[i,])[,1]) )
  }
  scatter <- as.data.frame(scatter)

  the.plot <- ggplot(data=scatter, mapping=aes(x,y)) +
    geom_hex(bins=35, show.legend = FALSE) +
    geom_line(data = data.frame("x"=1:length(truth), "y"=t(truth)), mapping=aes(x,y), colour="red") + # Truth
    #geom_smooth(method="loess", se=TRUE, level=0.95, color="orange") +
    #geom_point(size=0.1, color="white") + # individual points
    ylab("Number of agents in the system")+
    xlab("Iteration")+
    ggtitle(paste("Observation Interval =", obs, sep =' '))
  
  return(the.plot)
}
  
plots <- map2(samples, obIntervals, function(x, obInterval) density_plot(x, truth, obInterval))

```

Plot them:

```{r density.plot1, fig.width=11, fig.height=7, cache=TRUE}

# use grid.arrange() function to lay out the plots
do.call("grid.arrange", c(plots, ncol=length(obIntervals)/2))

```


##Plot Sample accuracy change

See how the sample accuracy changes (are later samples closer to the truth?)

```{r euclidean.distance, fig.width=9, fig.height=5}
# See if later samples are closer to the truth.
s <- samples[[which(obIntervals == 1)]] # Just look at those with an observation interval of 1
# Calculate the euclidean distance of the sample away from the truth and see how this changes with sample number
x1 <- as.vector(t(truth)) # truth as a vector (not a load of tibble columns)
euclidean.dist <- sapply(X=1:nrow(s), FUN=function(x) {  
  x2 <- as.vector(t(s[x,])) # A row from the samples as a vector
  return(dist(rbind(x1,x2))) # Return euclidean distance (https://stackoverflow.com/questions/5559384/euclidean-distance-of-two-vectors)
  }  )
plot(euclidean.dist)

```

_TODO: could calculate mean autocorrelation_

# Summary stats

Calculate some summary statistics.

```{r }

samples_Summary <- function(df, obInterval) {
  df <- as.data.frame(df)
  mean_range <- mean(apply(df, 2, function(x) max(x) - min(x)))
  median_range <-  median(apply(df, 2, function(x) max(x) - min(x)))
  mean_IQR <- mean(apply(df, 2, function(x) IQR(x)))
  median_IQR <- median(apply(df, 2, function(x) IQR(x)))
  mean_sd <- mean(apply(df, 2, function(x) sd(x)))
  median_sd <- median(apply(df, 2, function(x) sd(x)))
  data.frame(observation_Interval=obInterval,
             mean_sd=mean_sd, median_sd=median_sd,
             mean_IQR=mean_IQR, median_IQR=median_IQR,
             mean_range=mean_range, median_range=median_range
  )

}


summaryStats <- do.call("rbind", map2(samples, obIntervals, samples_Summary))
summaryStats

#write_csv(summaryStats, "observation_intervals_summary.csv")

```

Now see if the mean standard deviation varies with the observation interval. I.e. do we start to see more/less spread with fewer observations?

```{r plot.sample.spread }

plot(summaryStats$observation_Interval, summaryStats$mean_sd,
     main="Spread of samples", xlab="Observation interval", ylab="Mean Standard Deviation")

```

_I think we need more observations_
